### 2022-05-22 sections/papers.tex
Update papers.tex

\item{Fleming, T., González-Bustamante, B., \& Schleiter, P. (2022, {\itshape forthcoming}). Cabinet Reshuffles and Parliamentary No-Confidence Motions. {\itshape Government and Opposition}.}\vspace{1mm}

@@

@@

\begin{benumerate}{12}
\item{\small Gonz\'alez-Bustamante, B., \& Luci, F. (2021, {\itshape forthcoming}). Political Elites in Latin America: Socialisation, Trajectories, and Capitals. Introduction. {\itshape Pléyade, Revista de Humanidades y Ciencias Sociales}, 28. {\footnotesize \scshape [in Spanish]}. {\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/wud59}{\textcolor{blue}{10.31235/osf.io/wud59}}}\vspace{1mm}

>>>>

\item{Fleming, T. G., González-Bustamante, B., \& Schleiter, P. (2022, {\itshape forthcoming}). Cabinet Reshuffles and Parliamentary No-Confidence Motions. {\itshape Government and Opposition}.}\vspace{1mm}

@@

\begin{benumerate}{9}

\item{\small Cisternas, C., \& González-Bustamante, B. (2022, {\itshape forthcoming}). Social Sciences in Repression Contexts: Bibliometric Analysis of the Historical Production of the Corporación de Estudios para Latinoamérica (1979-1989). {\itshape e-Ciencias de la Información}. {\footnotesize \scshape [in Spanish]}.}\vspace{1mm}

@@

\begin{benumerate}{12}

\item{\small Gonz\'alez-Bustamante, B., \& Luci, F. (2021). Political Elites in Latin America: Socialisation, Trajectories, and Capitals. {\itshape Pléyade, Revista de Humanidades y Ciencias Sociales}, 28, 21--32. {\footnotesize \scshape [in Spanish]}. \\ {\scshape url:} \href{http://www.revistapleyade.cl/index.php/OJS/article/view/359}{\textcolor{blue}{www.revistapleyade.cl}}. {\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/wud59}{\textcolor{blue}{10.31235/osf.io/wud59}}}\vspace{1mm}
